upwell_IDX

### 2020-04-27 upwell_IDX.Rmd
update

# RWS: Please figure out why some wind direction values are returned as NA
# RWS: Also, it's not enough to just calculate mean speed. It needs to be taken into account with the directions.
# RWS: Please look through these resources and make corrections accordingly:
# https://cran.r-project.org/web/packages/rWind/rWind.pdfsave(, file = "Data_coastal_angle/wind_daily.RData")
# https://www.kaggle.com/srlightfoote/example-wind-analysis-in-r
# The data provided by SAWS already reads wind from the direction which it is blwing

>>>>

wind_daily_tested <- wind_data %>% 
  filter(temp_sites %in% selected_sites) %>%  # Matching the sites to wind temp sites
  dplyr::group_by(temp_sites, date)

#save(wind_daily_tested, file = "Data_coast_angle/wind_daily_tested.RData")

# RWS: Also, it's not enough to just calculate mean speed. It needs to be taken into account with the directions.
# RWS: Please look through these resources and make corrections accordingly:
# https://cran.r-project.org/web/packages/rWind/rWind.pdfsave(, file = "Data_coastal_angle/wind_daily.RData")
# https://www.kaggle.com/srlightfoote/example-wind-analysis-in-r
# The data provided by SAWS already reads wind from the direction which it is blwing

#AA: NA values appear when applying the circular function...
load(Data_coast_angle/wind_daily_tested.RData)
